%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
%Version for spanish users, by dgarhdez

\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage[spanish,es-lcroman]{babel}


% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Roy}{Luo}
\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{Markham, Ontario}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{4373634171}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{royluocanada@gmail.com}
\date{July 27, 2024}                              % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{\phantom{1}}{}
\opening{\phantom{1}}
\closing{\phantom{1}}
\enclosure[\phantom{1}]{\phantom{1}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

Dear Hiring Manager,

I am writing to express my interest in the Zebricks Data Intern position at Lumerate. I have a strong background in statistics and data analysis which is the focus of my studies at the University of Waterloo, I am eager to contribute to and learn from your innovative team.

In regards to the word at the coordinates given, I believe the word is 'CGI' although it may also be 'mattamyhomes'.

Lumerate’s mission to provide comprehensive industry intelligence aligns perfectly with my academic and career aspirations. I am particularly excited about the Zebricks platform and its role in facilitating meaningful connections between patient advocacy groups and life-science industry professionals. I am passionate about leveraging data to drive informed decision-making and believe my skills and interests make me an ideal candidate for this role.

During my studies, I have honed my abilities in qualitative and quantitative data analysis. My coursework and previous work experience has provided me with a solid foundation in statistical methods and the use of tools like Excel and Google Sheets, essential for meticulous data management. Furthermore, my curiosity drives me to continuously seek out new information and insights, a quality I believe is crucial for reviewing and analyzing news content from patient advocacy groups effectively.

I am also very tech-savvy and have gained some experience with Python, enhancing my ability to contribute to the machine learning processes that make data actionable for Zebricks users. Additionally, my organizational skills and ability to work independently will allow me to manage various tasks and projects efficiently, helping to shape data best practices within the team.

Beyond my technical skills, I am drawn to Lumerate's dynamic and innovative environment. The opportunity to work in a lean startup setting and contribute to new ideas is incredibly appealing. I am eager to learn and leverage machine learning tools to introduce efficiencies and solve complex data problems, aligning with my goal of exploring diverse career options and making a tangible impact in the tech industry.

I would be thrilled to bring my enthusiasm and expertise to Lumerate, contributing to your mission and growing alongside the Zebricks team.

Thank you for considering my application. I am excited about the possibility of contributing to your team and am available at your earliest convenience for an interview.

Best regards,

Roy Luo

\vspace{0.5cm}



\end{document}


%% end of file `template.tex'.
