\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=•]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kalene Wu} \\ \vspace{1pt}
    \small 437-223-8828 $|$ \href{mailto:kalenewu111@gmail.com}{\underline{kalenewu111@gmail.com}} $|$ Hamilton, ON
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {McMaster University}{Sep 2025 -- Present}
    {Bachelor of Engineering, Biomedical Engineering}{Hamilton, Ontario}
  \resumeItemListStart
    \resumeItem{Relevant Coursework: Biology, Physics, Linear Algebra, Engineering Design, Programming Fundamentals}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
   \textbf{Languages:} Python, MATLAB, R \\
   \textbf{Tools:} SolidWorks, Fusion 360, Arduino IDE, Excel, PowerPoint \\
   \textbf{Libraries:} pandas, NumPy, Matplotlib, scikit-learn \\
   \textbf{Areas of Interest:} Biomechanics, Medical Device Design, Bioinstrumentation, Rehabilitation Technology
   }}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading{\textbf{Modular Colostomy Bag Attachment Design} $|$ \emph{Fusion 360, Biomedical Design}}{}
  \resumeItemListStart
    \resumeItem{Collaborated in an interdisciplinary team to design modular attachments to improving comfort and hygiene for indivduals with stomas.}
    \resumeItem{Iterated multiple attachment geometries in \textbf{Fusion 360} and performed simulated pressure and sealing tests, achieving a 40\% reduction in leak rate.}
    \resumeItem{Integrated a silicone-based gasket for improved skin compatibility and airflow to minimize irritation.}
    \resumeItem{Collected qualitative feedback from two patients and a nurse practitioner to refine ergonomic curvature and alignment features.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{Heart Rate Monitoring System (Team of 3)} $|$ \emph{Arduino, Python}}{}
  \resumeItemListStart
    \resumeItem{Built a wearable heart rate sensor using Arduino and PPG module, processing over 2,000 signal samples per subject.}
    \resumeItem{Implemented a moving-average filter and peak-detection algorithm in Python to achieve $\pm$2 bpm accuracy.}
    \resumeItem{Visualized live readings in a Python dashboard tested across 10 participants with varying physical activity levels.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{3D-Printed Prosthetic Hand Prototype} $|$ \emph{Fusion 360, PLA Printing}}{}
  \resumeItemListStart
    \resumeItem{Designed and printed a tendon-driven prosthetic hand actuated by elastic cords with individual finger control.}
    \resumeItem{Conducted finite element analysis (FEA) to assess joint stress under 25 N applied load, improving structural efficiency by 20\%.}
    \resumeItem{Presented final model at McMaster Engineering Design Expo (2025) as part of a rehabilitation technology demonstration.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart


  \resumeSubheading
    {Hospital Co-op Student, Palliative Care Unit}{Sep 2023 -- Jan 2024}
    {Mackenzie Health Hospital (SHSM Program Partnership)}{Richmond Hill, ON}
  \resumeItemListStart
    \resumeItem{Worked alongside nurses and physicians to support the daily needs of 15+ palliative care patients with empathy and professionalism.}
    \resumeItem{Monitored and documented patient comfort levels, meal intake, and mobility using standardized care tracking sheets.}
    \resumeItem{Observed and assisted during wound dressing changes, IV maintenance, and patient repositioning procedures.}
    \resumeItem{Communicated with families and coordinated visits while maintaining patient confidentiality and compliance with infection control protocols.}
    \resumeItem{Participated in weekly safety briefings and infection prevention audits to reinforce WHMIS and hospital safety compliance.}
  \resumeItemListEnd

    \resumeSubheading
    {Lifesaving Instructor (Certified)}{Jun 2022 -- Aug 2023}
    {Lifesaving Society of Ontario}{Richmond Hill, ON}
  \resumeItemListStart
    \resumeItem{Delivered CPR, First Aid, and aquatic safety training to over 60 youth and adults, emphasizing emergency response procedures aligned with public health standards.}
    \resumeItem{Demonstrated and supervised rescue techniques, improving participant success rate on certification exams by 25\%.}
    \resumeItem{Integrated anatomical and physiological principles into lessons to explain the mechanisms of drowning, hypoxia, and resuscitation.}
    \resumeItem{Ensured WHMIS and Ontario Health \& Safety compliance during all instructional sessions, maintaining a zero-incident record.}
  \resumeItemListEnd



\resumeSubHeadingListEnd

% %-----------AWARDS-----------
% \section{Awards \& Certifications}
% \resumeSubHeadingListStart
%   \resumeItem{Top 1\% Nationally – University of Toronto National Biology Competition (2024)}
%   \resumeItem{SolidWorks Associate Certification (CSWA)}
%   \resumeItem{Workplace Hazardous Materials Information System (WHMIS) Certified}
%   \resumeItem{Health and Safety Awareness Certified (Ontario Ministry of Labour)}
%   \resumeItem{Certified Bilingual (French) – Diplôme d'Études en Langue Française (DELF) Level B2}
%   \resumeItem{First Aid \& CPR Certified}
%\resumeSubHeadingListEnd

\end{document}
